Global patterns of forest autotrophic carbon fluxes

### 2020-02-14 manuscript/manuscript draft.Rmd
removed methodological consistency section in methods
#56

@@

*Methodological consistency.* 
{**This whole section needs to be re-written.**} 
The data in ForC is derived from a range of studies, often employing different methods. For this reason, criteria were introduced to standardise for differences in methodology. Where data was based on forest plot census measurements, studies which used a minimum diameter at breast height (DBH) measure of >10cm were excluded from analysis.  It would be preferable to standardise by minimum area sampled; however x% of plots in the database are 1 ha or under in size; excluding these plots would place significant constraints on sample size. (**really, we didn't exclude any studies based on methodology (except soil respiration. all studies measured min DBH 10 or less... ), so this paragraph needs revision. Also, address whether we standardize for inclusion/ exclusion of recruitment.**)
- recruitment preferred when an option, did not review whether all included recruitment
- excluded alkali absoption and soda lime methods for estimating soil / root respiration

>>>>

- excluded alkali absoption and soda lime methods for estimating soil / root respiration

@@
